Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-10 hotstorage13/arch.tex
update figure 2

We consider deduplication in two levels. The first-level of data deduplication can be accomplished efficiently and 
inexpensively using a coarse-grain segment-level  dirty bit based detection in the OS level  to 
identify version difference from the previous snapshot to the current snapshot.  
Version-based detection has been used in the previous work~\cite{Clements2009,Vrable2009,TanIPDPS2011} and
we emphasize a segment-level coarse-grain setting to reduce the efforts in detection and maintaining dirty bits. 
Our experiment with Alibaba's production dataset shows that over 70 percentage of 
duplicates can be detected using segment-based dirty bits when the segment size is as large as 2M bytes.  
This setting requires OS to keep the metadata for segment dirty bits and the amount of space for such segment 
dirty bits is negligible. In the second level of deduplication, content blocks of dirty segments at each VM 
are compared with the fingerprints of unique  blocks from the previous snapshots.

@@

\begin{figure*}[tbhp]
\centering
\includegraphics[width=0.75\textwidth]{steps.pdf}
\caption{Processing flow of Phases 1  and 2.}
\label{fig:flow}
\end{figure*}

>>>>

We consider deduplication in two levels. The first-level of data deduplication can be accomplished efficiently and 
inexpensively using a coarse-grain segment-level  dirty bit based detection in the OS level  to 
identify version difference from the previous snapshot to the current snapshot.  
Version-based detection has been used in the previous work~\cite{Clements2009,cumulus09,TanIPDPS2011} and
we emphasize a segment-level coarse-grain setting to reduce the efforts in detection and maintaining dirty bits. 
Our experiment with Alibaba's production dataset shows that over 70 percentage of 
duplicates can be detected using segment-based dirty bits when the segment size is as large as 2M bytes.  
This setting requires OS to keep the metadata for segment dirty bits and the amount of space for such segment 
dirty bits is negligible. In the second level of deduplication, content blocks of dirty segments at each VM 
are compared with the fingerprints of unique  blocks from the previous snapshots.

@@

\begin{figure*}[tbhp]
\centering
\includegraphics[width=0.95\textwidth]{steps.pdf}
\caption{Processing flow of Phases 1  and 2.}
\label{fig:flow}
\end{figure*}
